Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2022-03-21 paper/response_memo.Rmd

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: ../svm-latex-ms2.tex
title: |
    | Public Gender Egalitarianism: A Dataset of Dynamic Comparative
  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: single
bibliography: dcpo_gender_roles.bib
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300)

# If you haven't install `DCPOtools`
# remotes::install_github("fsolt/DCPOtools")

if (!require(pacman)) install.packages("pacman")
library(pacman)
library(patchwork)
library(rsdmx)

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broom, tidyverse, janitor, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

```

Thank you for your helpful comments, as well as your general enthusiasm for this piece.
We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Introduction** R2 asked if we were "only using cross-national surveys or whether you also incorporate single-country surveys."
We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
We also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question in an effort to avoid any confusion.

1. **Estimating Public Gender Egalitarianism** R2 suggested that our description of the model could be made more accessible given the broad audience of the _BJPS_ and the work's potential for use in the classroom.
We agree entirely.
We revised these paragraphs carefully for readability, shifting much of the technical discussion to an online appendix and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.

Thank you once more for the opportunity to make revisions.
We think the paper is much stronger as a result of your comments; in fact, with your assistance, we think it lives up to R3's assessment as an "exemplary demonstration" of the role of replication in scientific progress.
We hope you all agree.

# References

<div id="refs"></div>

### 2022-03-21 paper/response_memo.Rmd

```

Thank you for your helpful comments, as well as your general enthusiasm for this piece.
We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Introduction** R2 asked if we were "only using cross-national surveys or whether you also incorporate single-country surveys."
We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
We also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question in an effort to avoid any confusion.

1. **Examining the Source Data on Public Gender Egalitarianism** R1 noted three spots in the first few pages where our language was respectively unclear, mistaken, and repeated.
We corrected each of these infelicities with gratitude.

1. **Estimating Public Gender Egalitarianism** R2 suggested that our description of the model could be made more accessible given the broad audience of the _BJPS_ and the work's potential for use in the classroom.
We agree entirely.
We revised these paragraphs carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.

1. **Estimating Public Gender Egalitarianism** R1 requested "more description about how the estimates were obtained," specifically details about iterations, chains, warmup, thinning, and convergence.  We added a short paragraph with this information at p5.

Thank you once more for the opportunity to make revisions.
We think the paper is much stronger as a result of your comments, and we hope you agree.

### 2022-03-23 paper/response_memo.Rmd

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: yes
    latex_engine: xelatex

title: |
  | Public Gender Egalitarianism:
  | A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere
subtitle: "Memo to Reviewers"

date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: single
bibliography: dcpo_gender_roles.bib
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

1. **Introduction** R2 asked if we were "only using cross-national surveys or whether you also incorporate single-country surveys."
We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
We also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question in an effort to avoid any confusion.

1. **Examining the Source Data on Public Gender Egalitarianism** R1 noted three spots in the first few pages where our language was respectively unclear, mistaken, and repeated.
We corrected each of these infelicities with gratitude.

1. **Estimating Public Gender Egalitarianism** R2 suggested that our description of the model could be made more accessible given the broad audience of the _BJPS_ and the work's potential for use in the classroom.
We agree entirely.
We revised these paragraphs carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.

1. **Estimating Public Gender Egalitarianism** Noting that the source data covers only "roughly 45 percent of the possible sample of country-years" and that it is decidedly unbalanced, R1 raised the question of whether this means that PGE estimates for country-years without source data were unavailable: if so, PGE would be limited in cross-national time-series applications due to listwise deletion and the complete series depicted in Figure 3 would be misleading.
This is an important question.
The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed for when survey data on the topic of interest is not available for all years in all countries, a problem referred to as sparsity.
So we do actually have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at p4-5.

@@

1. **Estimating Public Gender Egalitarianism** R1 requested "more description about how the estimates were obtained," specifically details about iterations, chains, warmup, thinning, and convergence.
We added a short paragraph with this information at p5.

We also took advantage of the opportunity to add more source data...

### 2022-03-23 paper/response_memo.Rmd

Thank you for your helpful comments, as well as your general enthusiasm for this piece.
We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Introduction** R2 asked if we were "only using cross-national surveys or whether you also incorporate single-country surveys."
We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
We also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question in an effort to avoid any confusion.

1. **Examining the Source Data on Public Gender Egalitarianism** R1 noted three spots in the first few pages where our language was respectively unclear, mistaken, and repeated.
We corrected each of these infelicities with gratitude.

1. **Estimating Public Gender Egalitarianism** R2 suggested that our description of the model could be made more accessible given the broad audience of the _BJPS_ and the work's potential for use in the classroom.
We agree entirely.
We revised these paragraphs (now at pp4-5) carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.

1. **Estimating Public Gender Egalitarianism** R1 noted that the source data covers only "roughly 45 percent of the possible sample of country-years" and that it is decidedly unbalanced, and raised the question of whether this means that PGE estimates for country-years without source data were unavailable: if so, PGE would be limited in cross-national time-series applications due to listwise deletion and the complete series depicted in Figure 3 would be misleading.
This is an important question.
The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed for when survey data on the topic of interest is not available for all years in all countries, a problem referred to as sparsity.
So we actually do have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at pp4-5.

1. **Estimating Public Gender Egalitarianism** R1 recommended including a discussion of difficulty and dispersion in the main text, and also suggested representing the estimates of these parameters in the text as in @Gandhi2020 [, 1552].
We now discuss difficulty and dispersion at p4 to explain how the DCPO model we adopt addresses the incomparability of the available survey data.
Regrettably, we were not able to able to carve out space in the text to represent and discuss the estimates of these parameters (understandable, we hope, given that we have some four times the number of indicators that @Gandhi2020 employed).
We present these parameters in Appendix A.

### 2022-03-23 paper/response_memo.Rmd

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

```

Thank you for your helpful comments, as well as your general enthusiasm for this piece.
We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Introduction** R2 asked if we were "only using cross-national surveys or whether you also incorporate single-country surveys."
We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
To try to avoid any confusion, we also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question.

@@

1. **Examining the Source Data on Public Gender Egalitarianism** R1 noted three spots in the first few pages where our language was respectively unclear, mistaken, and repeated.
We corrected each of these infelicities with gratitude.

1. **Estimating Public Gender Egalitarianism** R2 suggested that our description of the model could be made more accessible given the broad audience of the _BJPS_ and the work's potential for use in the classroom.
We agree entirely.
We revised these paragraphs (now at pages 4-5) carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.

1. **Estimating Public Gender Egalitarianism** R1 noted that the source data covers only "roughly 45 percent of the possible sample of country-years" and that it is decidedly unbalanced, and raised the question of whether this means that PGE estimates for country-years without source data were unavailable: if so, PGE would be limited in cross-national time-series applications due to listwise deletion and the complete series depicted in Figure 3 would be misleading.
This is an important question.
The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed for when survey data on the topic of interest is not available for all years in all countries, a problem referred to as sparsity.
So we actually do have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at pages 4-5.

1. **Estimating Public Gender Egalitarianism** R1 recommended including a discussion of difficulty and dispersion in the main text, and also suggested representing the estimates of these parameters in the text as in @Gandhi2020 [, 1552].
We now discuss difficulty and dispersion at page 4 to explain how the DCPO model we adopt addresses the incomparability of the available survey data.
Regrettably, we were not able to able to carve out space in the text to represent and discuss the estimates of these parameters (understandable, we hope, given that we have some four times the number of indicators that @Gandhi2020 employed).
We present these parameters in Appendix A.

### 2022-03-23 paper/dcpo_gender_roles.Rmd
update
clean up

Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.

@@

To address the sparsity of the source data---the fact that there are gaps in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses simple local-level dynamic linear models, i.e., random-walk priors, for each country.
That is, within each country, each year's value of public gender egalitarianism is modeled as the previous year's estimate plus a random shock.
These dynamic models smooth the estimates of public gender egalitarianism over time and allow estimation even in years for which little or no survey data is available, albeit at the expense of greater measurement uncertainty.

@@

```{r dcpo_results, cache=TRUE}
load(here::here("data", "poliwork_polileader4_2_4k_06-23.rda"))

@@

We estimated the model using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, discarding the first half as warmup, and thinning the remainder by eight, which left us with 1,000 samples.
The $\hat{R}$ diagnostic had a maximum value of 1.02, indicating the model converged.

@@

ggplot(data = c_rawdata, aes(x = year, y = mean)) +
  geom_line(aes(color = item, alpha = 1/alpha_mean)) +
  geom_point(aes(color = item, alpha = 1/alpha_mean)) +
  theme_bw() +
  theme(legend.position = "none") +
  coord_cartesian(xlim = c(1980, 2020), ylim = c(0, 1)) +
  labs(x = NULL, y = "PGE Scores") +
  geom_ribbon(data = c_res, aes(ymin = `10%`, ymax = `90%`, linetype=NA), alpha = .25) +
  geom_line(data = c_res) +
  facet_wrap(~country, nrow = 2) +
  theme(axis.text.x  = element_text(size=7,
                                    angle = 90,
                                    vjust = .45,
                                    hjust = .95),
        strip.background = element_rect(fill = "white", colour = "white")) +
  plot_annotation(caption = "Note: Countries are ordered by their PGE scores in their most recent\navailable year; gray shading represents 80% credible intervals.")
```

@@

Such future research, however, depends on the validity of the PGE scores.
Like @Caughey2019 [684-685], we provide evidence of our measure's validity with convergent validation and construct validation.
Figure&nbsp;\ref{conv_plot} displays our demonstrations of convergent validation.
Convergent validation refers to showing that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
Here, we compare PGE scores to responses to individual survey items that were included in the source data, that is, we provide an 'internal' validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In the left panel, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
Then, in the center panel, we look at the question that provides the most data-rich cross-section, which asked whether respondents felt "men generally make better political leaders than women" and was included in Pew Global's Spring 2007 survey.
Finally, in the right panel, to evaluate how well the PGE scores capture change over time, we focus on the item with the largest number of observations for a single country, which asked respondents to the U.S. General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."
In every case, the correlations---estimated taking into account the uncertainty in the measures---are in the expected direction and very strong.
<!-- ^[ -->
<!-- The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the political leadership question, but failing to account for this uncertainty would overstate the correlation with the Pew item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S. GSS item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`. -->
<!-- We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.] -->

@@

We continue, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Assuming that attitudes that women should prioritize housework and childcare over paid employment and politics---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE scores.
Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE scores.

>>>>

Consider the most frequently asked item in these data, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.

@@

To address the sparsity of the source data---the fact that there are gaps in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses local-level dynamic linear models, i.e., random-walk priors, for each country.
That is, within each country, each year's value of public gender egalitarianism is modeled as the previous year's estimate plus a random shock.
These dynamic models smooth the estimates of public gender egalitarianism over time and allow estimation even in years for which little or no survey data is available, albeit at the expense of greater measurement uncertainty.

@@

```{r dcpo_results, cache=TRUE}
load(here::here("data", "poliwork_polileader4_2_4k_02_16.rda"))

@@

We estimated the model on our source data using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, discarding the first half as warmup, and thinning the remainder by eight, which left us with 1,000 samples.
The $\hat{R}$ diagnostic had a maximum value of 1.02, indicating the model converged.

@@

# ggplot(data = c_rawdata, aes(x = year, y = mean)) +
#   geom_line(aes(color = item, alpha = 1/alpha_mean)) +
#   geom_point(aes(color = item, alpha = 1/alpha_mean)) +
ggplot(data = c_res, aes(x = year, y = mean)) +
  theme_bw() +
  theme(legend.position = "none") +
  coord_cartesian(xlim = c(1980, 2020), ylim = c(0, 1)) +
  labs(x = NULL, y = "PGE Scores") +
  geom_ribbon(data = c_res, aes(ymin = `10%`, ymax = `90%`, linetype=NA), alpha = .25) +
  geom_line(data = c_res) +
  facet_wrap(~country, nrow = 2) +
  theme(axis.text.x  = element_text(size=7,
                                    angle = 90,
                                    vjust = .45,
                                    hjust = .95),
        strip.background = element_rect(fill = "white", colour = "white")) +
  plot_annotation(caption = "Note: Countries are ordered by their PGE scores in their most recent\navailable year; gray shading represents 80% credible intervals.")
```

@@

Such future research, however, depends on the validity of the PGE scores.
Like @Caughey2019 [684-685], we provide evidence of our measure's validity with convergent validation and construct validation.
Convergent validation refers to showing that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
Here, we compare PGE scores to responses to individual source-data survey items that were used to generate our estimates, that is, we provide an 'internal' validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In the left panel of Figure&nbsp;\ref{conv_plot}, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
Then, in the center panel, we look at the question that provides the most data-rich cross-section in the source data, which asked whether respondents felt "men generally make better political leaders than women" and was included in Pew Global's Spring 2007 survey.
Finally, in the right panel, to evaluate how well the PGE scores capture change over time, we focus on the item with the largest number of observations for a single country in the source data, which asked respondents to the U.S. General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."
In every case, the correlations---estimated taking into account the uncertainty in the measures---are in the expected direction and very strong.
<!-- ^[ -->
<!-- The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the political leadership question, but failing to account for this uncertainty would overstate the correlation with the Pew item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S. GSS item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`. -->
<!-- We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.] -->

@@

We continue, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items not included in our source data but tapping a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Assuming that attitudes that women should prioritize housework and childcare over paid employment and politics---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE scores.
Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE scores.
